---
title: "Stock Price Analysis and Trading Strategies"
output: html_document
date: "2024-07-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(quantmod)
library(PerformanceAnalytics)
library(forecast)
library(xts)
```



```{r }
# Download stock data
getSymbols(c("AAPL", "TSLA", "MSFT"), auto.assign=TRUE)

# Convert to data frames and save
AAPL_data <- data.frame(getSymbols("AAPL", auto.assign=F))
TSLA_data <- data.frame(getSymbols("TSLA", auto.assign=F))
MSFT_data <- data.frame(getSymbols("MSFT", auto.assign=F))

# Assign column names
colnames(AAPL_data) <- c("Open", "High", "Low", "Close", "Volume", "Adjusted")
colnames(TSLA_data) <- c("Open", "High", "Low", "Close", "Volume", "Adjusted")
colnames(MSFT_data) <- c("Open", "High", "Low", "Close", "Volume", "Adjusted")

# Write to CSV
write.csv(AAPL_data, "AAPL-Data.csv")
write.csv(TSLA_data, "TSLA-Data.csv")
write.csv(MSFT_data, "MSFT-Data.csv")
```

```{r }
# Load data
AAPL <- read.csv("AAPL-Data.csv", row.names = 1)
TSLA <- read.csv("TSLA-Data.csv", row.names = 1)
MSFT <- read.csv("MSFT-Data.csv", row.names = 1)

# Convert data to xts objects
AAPL_xts <- as.xts(AAPL[, "Adjusted"], order.by = as.Date(row.names(AAPL)))
TSLA_xts <- as.xts(TSLA[, "Adjusted"], order.by = as.Date(row.names(TSLA)))
MSFT_xts <- as.xts(MSFT[, "Adjusted"], order.by = as.Date(row.names(MSFT)))

# Plotting
plot(AAPL_xts, main = "AAPL Adjusted Closing Prices", major.ticks = "years", minor.ticks = FALSE)
plot(TSLA_xts, main = "TSLA Adjusted Closing Prices", major.ticks = "years", minor.ticks = FALSE)
plot(MSFT_xts, main = "MSFT Adjusted Closing Prices", major.ticks = "years", minor.ticks = FALSE)
```
The adjusted closing prices for AAPL, TSLA, and MSFT reveal strong growth, especially after 2010. TSLA's dramatic increase post-2019 highlights its rapid market rise due to milestones in electric vehicle production.

```{r }
# Calculate daily returns
AAPL_returns <- dailyReturn(Ad(as.xts(AAPL)), type="arithmetic")
TSLA_returns <- dailyReturn(Ad(as.xts(TSLA)), type="arithmetic")
MSFT_returns <- dailyReturn(Ad(as.xts(MSFT)), type="arithmetic")

# Plot cumulative returns
plot(cumprod(1 + AAPL_returns), main="Cumulative Returns - AAPL", type='l')
plot(cumprod(1 + TSLA_returns), main="Cumulative Returns - TSLA", type='l')
plot(cumprod(1 + MSFT_returns), main="Cumulative Returns - MSFT", type='l')
```
The cumulative returns plots for AAPL, TSLA, and MSFT illustrate the compounded growth of an investment over time. They show substantial long-term gains, with AAPL and MSFT exhibiting steady growth post-2010, while TSLA demonstrates a sharp increase starting around 2019, reflecting significant investment returns due to their respective market performances.

```{r }
# Compare cumulative returns for AAPL
compareAdtoCl <- data.frame(apply(apply(AAPL[, c("Close", "Adjusted")], 2, log), 2, diff))
compareAdtoCumSum <- data.frame(apply(compareAdtoCl, 2, cumsum))
plot(compareAdtoCumSum[, 1], type='l', main="Cumulative Returns Comparison for AAPL", ylab="Cumulative Returns", xlab="Index")
lines(compareAdtoCumSum[, 2], type='l', col='blue')
legend("topleft", legend=c("Close", "Adjusted"), col=c("black", "blue"), lty=1)

# Performance Summary for AAPL
data <- as.xts(compareAdtoCl)
data <- exp(data) - 1
charts.PerformanceSummary(data, main="Performance Summary - AAPL")

# Compare cumulative returns for MSFT
compareAdtoCl_MSFT <- data.frame(apply(apply(MSFT[, c("Close", "Adjusted")], 2, log), 2, diff))
compareAdtoCumSum_MSFT <- data.frame(apply(compareAdtoCl_MSFT, 2, cumsum))
plot(compareAdtoCumSum_MSFT[, 1], type='l', main="Cumulative Returns Comparison for MSFT", ylab="Cumulative Returns", xlab="Index")
lines(compareAdtoCumSum_MSFT[, 2], type='l', col='blue')
legend("topleft", legend=c("Close", "Adjusted"), col=c("black", "blue"), lty=1)

# Performance Summary for MSFT
data_MSFT <- as.xts(compareAdtoCl_MSFT)
data_MSFT <- exp(data_MSFT) - 1
charts.PerformanceSummary(data_MSFT, main="Performance Summary - MSFT")

# Compare AAPL and MSFT
AAPL_returns <- dailyReturn(Ad(as.xts(AAPL)), type="arithmetic")
MSFT_returns <- dailyReturn(Ad(as.xts(MSFT)), type="arithmetic")
colnames(AAPL_returns) <- "AAPL"
colnames(MSFT_returns) <- "MSFT"
AAPLvsMSFT <- merge(AAPL_returns, MSFT_returns, all = F)
charts.PerformanceSummary(AAPLvsMSFT)
table.AnnualizedReturns(AAPLvsMSFT, scale = 252, Rf = 0.005 / 252)
```
The plot of cumulative returns and performance summaries show that both AAPL and MSFT have experienced significant growth over the period, with AAPL generally outperforming MSFT. The annualized returns table further confirms AAPL's superior performance in terms of both returns and risk-adjusted returns. However, AAPL also exhibits higher volatility, which is reflected in its higher standard deviation.

```{r }
# Calculate rolling variance
AAPL_roll_var <- rollapply(AAPL_returns, width=30, FUN=var, by.column=TRUE, fill=NA)
plot(AAPL_roll_var, main="Rolling Variance - AAPL", type='l')

# Risk management using VaR
VaR(AAPL_returns, p=0.95, method="historical")
ES(AAPL_returns, p=0.95, method="historical")
```
The rolling variance plot indicates periods of high and low volatility in AAPL's returns, with significant spikes during major market disruptions like the 2008 financial crisis and the 2020 COVID-19 pandemic. The risk management metrics, VaR and ES, provide insights into potential daily losses, with VaR indicating a 2.94% maximum expected loss at 95% confidence and ES showing an average loss of 4.56% on days when losses exceed the VaR threshold. 

```{r }
# Fit ARIMA model
AAPL_arima <- auto.arima(Ad(as.xts(AAPL)))
summary(AAPL_arima)

# Forecast
AAPL_forecast <- forecast(AAPL_arima, h=30)
plot(AAPL_forecast)
```
The ARIMA(5,2,0) model for AAPL predicts a continued upward trend with low forecast errors, indicating a good fit. The prediction intervals highlight the uncertainty but suggest overall price growth in the next 30 days.
